Garbage Collection Evaluation Infrastructure\\ for the Cog VM

### 2018-06-20 paper.tex

We built two benchmarks out of the potential configurations:
\begin{itemize}
%\item \emph{FragmentedHeap:} First, objects are allocated on the heap, and some of them are released, leading to potential memory fragmentation. Then, new objects with a minimum size greater than the new free chunks sizes are allocated.
\item \emph{LargeObjects:} Only large objects with a size greater than 65535 32-bit machine words are allocated on the heap. These objects are allocated directly in the old space.
\item \emph{Data0bjects:} The majority of the objects that will be allocated on the heap will be Data objects, which will only contain one-byte-sized integers in this benchmark. Data Objects are raw data objects, which can be used, for example, to store characters, restricted-range integers, floats, etc: the garbage collector will not go through their slots in the marking phase.
\end{itemize}

@@

%\paragraph{FragmentedHeap.} The fragmented heap benchmark allocates objects of 300 slots maximum, releases half of them, and re-allocates half of the amount of objects with a minimum size of 600 slots.

\paragraph{LargeObjects.} The LargeObjects benchmark allocates objects larger than 65535 32-bits machine words. The time spent in scavenges is therefore lower than with smaller objects (that are not allocated in the old space at first). Allocating large objects has an impact on the number operations of memory growing and shrinking, which can be lowered by tuning the associated parameters in the VM. In this example, the New-Mem cases have memory segments four times bigger, and four empty segments are available instead of one.
\paragraph{Data0bjects.} The DataObjects benchmark allocates a large amount of data objects on the heap (90\% of all allocated objects during the benchmark). The time spent in full GC's and the compaction time are lower in comparison with a case with 40\% of Data Objects. This can be explained because less time is spent in the marking and pointer update phases.

>>>>

We built two benchmarks out of the potential configurations:
\begin{itemize}
\item \emph{LargeObjects:} Only large objects with a size greater than 65535 32-bit machine words are allocated on the heap. These objects are allocated directly in the old space.
\item \emph{Data0bjects:} The majority of the objects that will be allocated on the heap will be Data objects, which will only contain one-byte-sized integers in this benchmark. Data Objects are raw data objects, which can be used, for example, to store characters, restricted-range integers, floats, etc: the garbage collector will not go through their slots in the marking phase.
\end{itemize}

@@

\paragraph{LargeObjects.} The LargeObjects benchmark allocates objects larger than 65535 32-bit machine words. The time spent in scavenging is therefore lower. Allocating large objects has an impact on the number of memory growing and shrinking operations, which can be altered by tuning the associated parameters in the VM. 
\paragraph{Data0bjects.} The DataObjects benchmark allocates a large amount of data objects on the heap (90\% of all allocated objects during the benchmark). The time spent in full GC's and the compaction time are lower in comparison with a case with 40\% of Data Objects. This can be explained because less time is spent in the marking and pointer update phases.
